Comparing Power Optimizations in the Reorder Buffer

### 2011-06-08 paper/proj.tex
paper stuff.

As a few minor changes to the behavioral function of the OOP ROB, the first of which is the lack of the ability to forward operands.  Thus in the simulated stage of reading from the instruction
stream, when we would normally check if the operand is in the ROB and forward.  We instead do the following, we still check to see if the operand is in the ROB, and the retention latches. 
If the entry is not in the ROB, or the latches, the operand would be available in the ARF or memory, in the converse case,  the entry in both, the ROB, and the latches, the operand is forwarded
from the latches and the counter is incremented .  In the case that the entry exists in the ROB, but not in the latches, a flag would be set in the ROB to forward the result when committing to the ARF. 
The last case, that is the entry exists in the latches and not in the ROB, means that the result has already been committed and the result could be forwarded from the ARF.  Next in our update entries 
(when the cycle counter expires -- execution has completed) we would add in the new entry to the retention latch.  Lastly when the ROB entires are valid, and ready to be committed to the ARF,
if the forwarding flag is set, the forwarding counter is incremented.
\subsection{Power Tabulation Implementation}

>>>>

As a few minor changes to the behavioral function of the OOP ROB, the first of which is the lack of the ability to forward operands.  Thus in the simulated stage of reading from the instruction
stream, when we would normally check if the operand is in the ROB and forward.  We instead do the following, we still check to see if the operand is in the ROB, and the retention latches. 
If the entry is not in the ROB, or the latches, the operand would be available in the ARF or memory, in the converse case,  the entry in both, the ROB, and the latches, the operand is forwarded
from the latches and the counter is incremented .  In the case that the entry exists in the ROB, but not in the latches, a flag would be set in the ROB to forward the result when committing to the ARF. 
The last case, that is the entry exists in the latches and not in the ROB, means that the result has already been committed and the result could be forwarded from the ARF.  Next in our update entries 
(when the cycle counter expires -- execution has completed) we would add in the new entry to the retention latch.  Lastly when the ROB entires are valid, and ready to be committed to the ARF,
if the forwarding flag is set, the forwarding counter is incremented.
\subsection{Power Tabulation Implementation}
In order for our simulation to determine the power utilization, we do not try and equate each event with an associated cost in joules.  As technology changes, and new techniques are 
developed to decease circuit level power usages, our simulation will become less and less accurate.  Instead we chose to simply tabulate each event that is associated with 
power cost, such as bit flips from 0 to 1, register comparator usage, and bit lines driven.  To help measure leakage power and overall states of the ROB, we also keep track of the 
time (in cycles) each bit stays in the high state, or the low state.

At the start of each cycle
